Statistically-estimated tree composition for the northeastern United States \\ at the time of Euro-American settlement

### 2016-02-12 paperPlos.tex
final minor typo changes requested by PLOS ONE to paperPlos

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Statistically-estimated Tree Composition for the\\
Northeastern United States at Euro-American Settlement}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Christopher J. Paciorek\textsuperscript{1,*},
Simon J. Goring\textsuperscript{2,\Yinyang},
Andrew L. Thurman\textsuperscript{3,\Yinyang},
Charles V. Cogbill\textsuperscript{4},
John W. Williams\textsuperscript{2,5},
David J. Mladenoff\textsuperscript{6},
Jody A. Peters\textsuperscript{7},
Jun Zhu\textsuperscript{8},
Jason S. McLachlan\textsuperscript{7,\ddag}
\\
\bigskip
\bf{1} Department of Statistics, University of California, Berkeley, California,
USA
\\
\bf{2} Department of Geography, University of Wisconsin, Madison, Wisconsin,
USA
\\
\bf{3} Department of Statistics, University of Iowa, Iowa City, Iowa, USA
\\
\bf{4} Harvard Forest, Harvard University, Petersham, Massachusetts, USA
\\
\bf{5} Center for Climatic Research, University of Wisconsin, Madison,
Wisconsin, USA
\\
\bf{6} Department of Forest and Wildlife Ecology, University of Wisconsin,
Madison, Wisconsin, USA
\\
\bf{7} Department of Biological Sciences, University of Notre Dame, Notre
Dame, Indiana, USA
\\
\bf{8} Department of Statistics, University of Wisconsin, Madison, Wisconsin,
USA
\\
\bigskip

@@

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
 \ddag PI of the PalEON Project

@@

In \emph{Data} we describe the data sources, while in \emph{Statistical model} we describe 
the statistical model used to create the data product. In In \emph{Model comparison}
 we quantitatively compare competing
statistical specifications, and in \emph{Data Product}
we describe the final data product. In \emph{Discussion}
we discuss the uncertainties estimated by and the
limitations of the statistical model, and we list related data products
under development.

@@

Extensive details on the upper Midwest (Minnesota, Wisconsin, Michigan)
data and processing steps are available \cite{goring2015composition};
key elements include the use of only corner points, the use of only
the two closest trees at each corner point, spatially-varying correction
factors for sampling effort, and a standardized taxonomy table. The
lower Midwest (Illinois, Indiana) data were purchased from the Indiana
State Archives (Indiana) and Hubtack Document Resources (hubtack.com;
Illinois) and processed using similar steps as for the upper Midwest
data. Digitization of the Illinois and Indiana data is still underway,
so many grid cells contained no data at the time the statistical model
was fit. Note that the number of trees per grid cell varies depending
on the number of survey points in a cell, with an average of 124 trees
per cell. The gridded data at the 8 km resolution for the midwest
subdomain are available through the NIS data portal as
DOI:10.5072/FK2/e9c144ab83af70e29b8d6647aaae58f5 \cite{Gori:etal:data:2016}.
The TPS data were compiled by C.V. Cogbill from a myriad of archival
sources representing land division surveys conducted in connection
with local settlement and are available through the
NIS data portal as DOI:10.5072/FK2/4d44aebe71dbf65290d8ce1bde03598b
and DOI:10.5072/FK2/88e167487b22d5f657e7ce7e033772e1 \cite{Cogb:dataNE:2016,Cogb:dataOH:2016}.

@@

Gaussian processes are generally constructed using
one of a number of correlation functions that define how the strength
of correlation between the values of the process at two locations
decays as a function of the distance between the locations. We consider
Gaussian processes in the commonly-used \matern
class, using the following parameterization of the \matern correlation
function, 
\begin{equation}
R(d)=\frac{1}{\Gamma(\nu)2^{\nu-1}}\left(\frac{2\sqrt{\nu}d}{\rho}\right)^{\nu}\mathcal{K}_{\nu}\left(\frac{2\sqrt{\nu}d}{\rho}\right),\label{eq:Matern}
\end{equation}
where $d$ is Euclidean distance, $\rho$ is the spatial range parameter,
and $\mathcal{K}_{\nu}(\cdot)$ is the modified Bessel function of
the second kind, whose order is the smoothness (differentiability)
parameter, $\nu>0$. $\nu=0.5$ gives the exponential covariance.
For any pair of locations, $R(d)$ defines the correlation of the
process, (i.e., $\alpha_{p}(s)$ in our context), as a function of
the distance between the locations. Considering all pairs of locations,
this defines a correlation matrix for all locations of interest.

@@

The full description of the MCMC sampling steps is provided in the
\nameref{SI}. In addition, in the latent variable representation, $\theta_{p}(s)$
never appears explicitly and cannot be calculated in close form. Instead
we use Monte Carlo integration over $W_{ijp},\, p=1,\ldots,P$ to
estimate $\theta_{p}(s_{i})$, also described in the \nameref{SI}.

@@

For this final data product, we ran the model using the CAR specification
with all of the data (including the data held out
in the model comparison analyses) for 150,000 iterations with the
same burn-in and subsampling details as described in Section \ref{sec:Model-comparison}.
Based on graphical checks and calculation of effective sample size
values, mixing was generally reasonable, but for some of the hyperparameters
was relatively slow, particularly for less common taxa. Despite this,
mixing for the variables of substantive interest -- the proportions
-- was good, with effective sample sizes for the final product generally
near 250.

@@

The data product is publicly available at the NIS
Data Portal as DOI:10.5072/FK2/dfc5e9748c8df4c3c275eab0f42d9744 under
the CC BY 4.0 license as version 0.4 as of January 2016 \cite{paci:etal:data:2016}.
The product is in the form of a netCDF-4 file, with dimensions x-coordinate,
y-coordinate, and MCMC iteration. There is one variable per taxon.
In addition, dynamic visualizations of the product using the Shiny
tool are available at \href{https://www3.nd.edu/~paleolab/paleonproject/maps}{https://www3.nd.edu/$\sim$paleolab/paleonproject/maps}.
The PalEON Project (in particular the first author) will continue
to maintain this product, releasing new versions as additional data
in Illinois, Indiana and Ohio are digitized. Note that digitization
of data from Illinois and Indiana is ongoing, and digitization of
additional data from Ohio is planned as well. As a result, at some
point we expect to have complete data for the midwestern half of the
domain.

@@

\section*{S1 Appendix}
\label{SI}

@@

{\bf Define $\bar{w}_{ip}=\frac{1}{n_{i}}{\displaystyle \sum_{j=1}^{n_{i}}W_{ijp}}$
as the average of the $W$ values for the \emph{p}th taxon in the \emph{i}th
grid cell and $\bar{w}_{p}=\{\bar{w}_{ip}\},$ $i=1,\ldots,m$.} Let
$A$ be a diagonal matrix where $A_{ii}$ is the number of trees in
the \emph{i}th grid cell. When there are no trees in a grid cell, $\bar{w}_{ip}=0$
and $A_{ii}=0$. For the township data, at each iteration, based on
the current values of the grid cell membership variables, $\{c_{tj}\}$,
trees are aggregated into grid cells and the calculations above can
then be carried out.

@@

\begin{align}
W_{ijp} & \sim\begin{cases}
\mbox{TN}\big({\displaystyle \max_{p^{*}\neq y_{ij}}w_{ijp^{*}},\infty,\alpha_{y_{ij}}(s_{i}),1\big),} & \mbox{if }p\mbox{ = \ensuremath{y_{ij}}}\\
\mbox{TN}\big(-\infty,w_{ijy_{ij}},\alpha_{p}(s_{i}),1\big), & \mbox{if }p\mbox{ \ensuremath{\neq y_{ij}}}
\end{cases}
\end{align}
In essence, the truncation value is determined by the taxon of the
\emph{j}th tree. For a given \emph{p}, the $W$ values for all trees in all
cells can be sampled in parallel.

The conditional distribution of $\alpha_{p}$ is 
\begin{align}
\alpha_{p} & \sim\N\bigg(\Big(A+Q_{p}\Big)^{-1}A\bar{w}_{p},\Big(A+Q_{p}\Big)^{-1}\bigg).
\end{align}
where $Q_{p}=(\sigma_{p}^{2})^{-1}Q$ for the CAR model and $\left(\sigma_{p}^{2}\cdot\frac{4\pi}{\rho_{p}^{2}}\right)^{-1}Q(\rho_{p})$
for the SPDE model. For each hyperparameter, $\phi_{p}=\log\sigma_{p}$
for the CAR model and $\phi_{p}\in\{\mu_{p},(\log\sigma_{p},\log\rho_{p})\}$
for the SPDE model, we sample $\{\phi_{p},\alpha_{p}\}$ jointly,
proposing $\phi_{p}$ as a random walk and, conditional on the proposed
value of $\phi_{p}$, sampling $\alpha_{p}$ from the distribution
just above. The joint proposal is accepted or rejected as a standard
Metropolis-Hastings proposal, with adaptation of the proposal (co)variance
\cite{Shab:Well:2011}. The proposal distribution for $\phi_{p}$
is a normal distribution (bivariate for $\phi_{p}=(\log\sigma_{p},\log\rho_{p})$).

@@

\subsection*{Estimating $\theta_{p}(s)$ via Monte Carlo integration}
\label{SI1}
{\bf In the latent variable representation, $\theta_{p}(s)$ never appears
explicitly and cannot be calculated in closed form.} Instead we use
Monte Carlo integration over $W_{ijp},\, p=1,\ldots,P$ to estimate
$\theta_{p}(s_{i})$. The quantity $\theta_{p}(s_{i})=\mbox{Prob}(W_{ijp}={\displaystyle \max_{p^{*}}W_{ijp^{*}})}$
defines the probability of taxon \emph{p} at grid cell \emph{i}. This requires
one to choose the number of Monte Carlo samples, which we set at 10000,
effectively sampling 10000 hypothetical trees and estimating the probabilities
of the different taxa in the population from the empirical proportions
in this sample of trees. For each of the saved MCMC samples, $k=1,\ldots K$,
we estimate $\theta_{p}^{(k)}(s_{i})$ numerically. Specifically,
for $t=1,\ldots,10000$ samples (i.e., hypothetical trees), we independently
draw
\[
W_{itp}^{(k)}\sim\N(\alpha_{p}^{(k)}(s_{i}),1),\, p=1,\ldots,P
\]
and estimate using 
\[
\theta_{p}^{(k)}(s_{i})\approx\frac{1}{10000}{\displaystyle \sum_{t=1}^{10000}1(W_{itp}^{(k)}={\displaystyle \max_{p^{*}}W_{itp^{*}}^{(k)})}},\, p=1,\ldots,P
\]
where $1(\cdot)$ is the indicator function that evaluates to 1 if
the expression is true and 0 if false. In other words, we calculate
the proportion of times that the maximum of $W_{itp},\, p=1,\ldots,P$
corresponds to taxon \emph{p}. Considering $\theta_{p}^{(k)}(s_{i}),\, k=1,\ldots,K$,
we have a sample from the posterior of $\theta_{p}(s_{i})$.

@@

\bibitem{pattison1957beginnings}
Pattison WD, et~al.
\newblock Beginnings of the American rectangular land survey system, 1784-1800.
\newblock Chicago: University of Chicago; 1957.

@@

\bibitem{gray2012forest}
Gray AN, Brandeis TJ, Shaw JD, McWilliams WH, Miles PD, et~al.
\newblock Forest Inventory and Analysis Database of the {United States} of
  {America} ({FIA}).
\newblock Vegetation databases for the 21st century--Biodiversity \& Ecology.
  2012;4:255--264.

@@

\bibitem{Gori:etal:data:2016}
Goring SJ, {University of Wisconsin}.
\newblock Settlement-era gridded tree composition, midwestern {US}: Level 1.
\newblock Long Term Ecological Research Network Data Portal; 2016. Paleon.2.0.

\bibitem{Cogb:dataNE:2016}
Cogbill CV.
\newblock Settlement-era tree composition, eastern {US}: level 1.
\newblock Long Term Ecological Research Network Data Portal; 2016. Paleon.4.11.

\bibitem{Cogb:dataOH:2016}
Cogbill CV.
\newblock Settlement-era tree composition, {O}hio: level 1.
\newblock Long Term Ecological Research Network Data Portal; 2016. Paleon.5.11.

@@

\bibitem{paci:etal:data:2016}
Paciorek CJ, Goring SJ, Thurman AL, Cogbill CV, Williams JW, Mladenoff DJ,
  et~al.
\newblock Settlement-era gridded tree composition, northeastern {US}: level 2.
\newblock Long Term Ecological Research Network Data Portal; 2016. Paleon.1.2.

>>>>

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Statistically-estimated Tree Composition for the\\
Northeastern United States at Euro-American Settlement}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Christopher J. Paciorek\textsuperscript{1,*},
Simon J. Goring\textsuperscript{2,\Yinyang},
Andrew L. Thurman\textsuperscript{3,\Yinyang},
Charles V. Cogbill\textsuperscript{4},
John W. Williams\textsuperscript{2,5},
David J. Mladenoff\textsuperscript{6},
Jody A. Peters\textsuperscript{7},
Jun Zhu\textsuperscript{8},
Jason S. McLachlan\textsuperscript{7}
\\
\bigskip
\bf{1} Department of Statistics, University of California, Berkeley, California,
USA
\\
\bf{2} Department of Geography, University of Wisconsin, Madison, Wisconsin,
USA
\\
\bf{3} Department of Statistics, University of Iowa, Iowa City, Iowa, USA
\\
\bf{4} Harvard Forest, Harvard University, Petersham, Massachusetts, USA
\\
\bf{5} Center for Climatic Research, University of Wisconsin, Madison,
Wisconsin, USA
\\
\bf{6} Department of Forest and Wildlife Ecology, University of Wisconsin,
Madison, Wisconsin, USA
\\
\bf{7} Department of Biological Sciences, University of Notre Dame, Notre
Dame, Indiana, USA
\\
\bf{8} Department of Statistics, University of Wisconsin, Madison, Wisconsin,
USA
\\
\bigskip

@@

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.

@@

In \emph{Data} we describe the data sources, while in \emph{Statistical model} we describe 
the statistical model used to create the data product. In \emph{Model comparison}
 we quantitatively compare competing
statistical specifications, and in \emph{Data Product}
we describe the final data product. In \emph{Discussion}
we discuss the uncertainties estimated by and the
limitations of the statistical model, and we list related data products
under development.

@@

Extensive details on the upper Midwest (Minnesota, Wisconsin, Michigan)
data and processing steps are available \cite{goring2015composition};
key elements include the use of only corner points, the use of only
the two closest trees at each corner point, spatially-varying correction
factors for sampling effort, and a standardized taxonomy table. The
lower Midwest (Illinois, Indiana) data were purchased from the Indiana
State Archives (Indiana) and Hubtack Document Resources (hubtack.com;
Illinois) and processed using similar steps as for the upper Midwest
data. Digitization of the Illinois and Indiana data is still underway,
so many grid cells contained no data at the time the statistical model
was fit. Note that the number of trees per grid cell varies depending
on the number of survey points in a cell, with an average of 124 trees
per cell. The gridded data at the 8 km resolution for the midwest
subdomain are available through the NIS data portal as
DOI:10.6073/pasta/aa0ef9828d41569a96651b056ad89fb3 \cite{Gori:etal:data:2016}.
The TPS data were compiled by C.V. Cogbill from a myriad of archival
sources representing land division surveys conducted in connection
with local settlement and are available through the
NIS data portal as DOI:10.6073/pasta/e40c1ad172882d5113844296611451f6
and DOI:10.6073/pasta/d09bb56c6af8ef0783cd7e76f8113b34 \cite{Cogb:dataNE:2016,Cogb:dataOH:2016}.

@@

Gaussian processes are generally constructed using
one of a number of correlation functions that define how the strength
of correlation between the values of the process at two locations
decays as a function of the distance between the locations. We consider
Gaussian processes in the commonly-used \matern
class, using the following parameterization of the \matern correlation
function, 
\begin{equation}
R(d)=\frac{1}{\Gamma(\nu)2^{\nu-1}}\left(\frac{2\sqrt{\nu}d}{\rho}\right)^{\nu}\mathcal{K}_{\nu}\left(\frac{2\sqrt{\nu}d}{\rho}\right),\nonumber
\end{equation}
where $d$ is Euclidean distance, $\rho$ is the spatial range parameter,
and $\mathcal{K}_{\nu}(\cdot)$ is the modified Bessel function of
the second kind, whose order is the smoothness (differentiability)
parameter, $\nu>0$. $\nu=0.5$ gives the exponential covariance.
For any pair of locations, $R(d)$ defines the correlation of the
process, (i.e., $\alpha_{p}(s)$ in our context), as a function of
the distance between the locations. Considering all pairs of locations,
this defines a correlation matrix for all locations of interest.

@@

The full description of the MCMC sampling steps is provided in \emph{Appendix}. In addition, in the latent variable representation, $\theta_{p}(s)$
never appears explicitly and cannot be calculated in close form. Instead
we use Monte Carlo integration over $W_{ijp},\, p=1,\ldots,P$ to
estimate $\theta_{p}(s_{i})$, also described in \emph{Appendix}.

@@

For this final data product, we ran the model using the CAR specification
with all of the data (including the data held out
in the model comparison analyses) for 150,000 iterations with the
same burn-in and subsampling details as described in \emph{Model comparison}.
Based on graphical checks and calculation of effective sample size
values, mixing was generally reasonable, but for some of the hyperparameters
was relatively slow, particularly for less common taxa. Despite this,
mixing for the variables of substantive interest -- the proportions
-- was good, with effective sample sizes for the final product generally
near 250.

@@

The data product is publicly available at the NIS
Data Portal as DOI:10.6073/pasta/8544e091b64db26fdbbbafd0699fa4f9 under
the CC BY 4.0 license as version 0.4 as of January 2016 \cite{paci:etal:data:2016}.
The product is in the form of a netCDF-4 file, with dimensions x-coordinate,
y-coordinate, and MCMC iteration. There is one variable per taxon.
In addition, dynamic visualizations of the product using the Shiny
tool are available at \href{https://www3.nd.edu/~paleolab/paleonproject/maps}{https://www3.nd.edu/$\sim$paleolab/paleonproject/maps}.
The PalEON Project (in particular the first author) will continue
to maintain this product, releasing new versions as additional data
in Illinois, Indiana and Ohio are digitized. Note that digitization
of data from Illinois and Indiana is ongoing, and digitization of
additional data from Ohio is planned as well. As a result, at some
point we expect to have complete data for the midwestern half of the
domain.

@@

\section*{Appendix}
\label{SI}

@@

Define $\bar{w}_{ip}=\frac{1}{n_{i}}{\displaystyle \sum_{j=1}^{n_{i}}W_{ijp}}$
as the average of the $W$ values for the \emph{p}th taxon in the \emph{i}th
grid cell and $\bar{w}_{p}=\{\bar{w}_{ip}\},$ $i=1,\ldots,m$. Let
$A$ be a diagonal matrix where $A_{ii}$ is the number of trees in
the \emph{i}th grid cell. When there are no trees in a grid cell, $\bar{w}_{ip}=0$
and $A_{ii}=0$. For the township data, at each iteration, based on
the current values of the grid cell membership variables, $\{c_{tj}\}$,
trees are aggregated into grid cells and the calculations above can
then be carried out.

@@

\begin{align}
W_{ijp} & \sim\begin{cases}
\mbox{TN}\big({\displaystyle \max_{p^{*}\neq y_{ij}}w_{ijp^{*}},\infty,\alpha_{y_{ij}}(s_{i}),1\big),} & \mbox{if }p\mbox{ = \ensuremath{y_{ij}}}\\
\mbox{TN}\big(-\infty,w_{ijy_{ij}},\alpha_{p}(s_{i}),1\big), & \mbox{if }p\mbox{ \ensuremath{\neq y_{ij}}}
\end{cases} \nonumber
\end{align}
In essence, the truncation value is determined by the taxon of the
\emph{j}th tree. For a given \emph{p}, the $W$ values for all trees in all
cells can be sampled in parallel.

The conditional distribution of $\alpha_{p}$ is 
\begin{align}
\alpha_{p} & \sim\N\bigg(\Big(A+Q_{p}\Big)^{-1}A\bar{w}_{p},\Big(A+Q_{p}\Big)^{-1}\bigg). \nonumber
\end{align}
where $Q_{p}=(\sigma_{p}^{2})^{-1}Q$ for the CAR model and $\left(\sigma_{p}^{2}\cdot\frac{4\pi}{\rho_{p}^{2}}\right)^{-1}Q(\rho_{p})$
for the SPDE model. For each hyperparameter, $\phi_{p}=\log\sigma_{p}$
for the CAR model and $\phi_{p}\in\{\mu_{p},(\log\sigma_{p},\log\rho_{p})\}$
for the SPDE model, we sample $\{\phi_{p},\alpha_{p}\}$ jointly,
proposing $\phi_{p}$ as a random walk and, conditional on the proposed
value of $\phi_{p}$, sampling $\alpha_{p}$ from the distribution
just above. The joint proposal is accepted or rejected as a standard
Metropolis-Hastings proposal, with adaptation of the proposal (co)variance
\cite{Shab:Well:2011}. The proposal distribution for $\phi_{p}$
is a normal distribution (bivariate for $\phi_{p}=(\log\sigma_{p},\log\rho_{p})$).

@@

\subsection*{Estimating $\theta_{p}(s)$ via Monte Carlo integration}
\label{SI1}
In the latent variable representation, $\theta_{p}(s)$ never appears
explicitly and cannot be calculated in closed form. Instead we use
Monte Carlo integration over $W_{ijp},\, p=1,\ldots,P$ to estimate
$\theta_{p}(s_{i})$. The quantity $\theta_{p}(s_{i})=\mbox{Prob}(W_{ijp}={\displaystyle \max_{p^{*}}W_{ijp^{*}})}$
defines the probability of taxon \emph{p} at grid cell \emph{i}. This requires
one to choose the number of Monte Carlo samples, which we set at 10000,
effectively sampling 10000 hypothetical trees and estimating the probabilities
of the different taxa in the population from the empirical proportions
in this sample of trees. For each of the saved MCMC samples, $k=1,\ldots K$,
we estimate $\theta_{p}^{(k)}(s_{i})$ numerically. Specifically,
for $t=1,\ldots,10000$ samples (i.e., hypothetical trees), we independently
draw
\[
W_{itp}^{(k)}\sim\N(\alpha_{p}^{(k)}(s_{i}),1),\, p=1,\ldots,P
\]
and estimate using 
\[
\theta_{p}^{(k)}(s_{i})\approx\frac{1}{10000}{\displaystyle \sum_{t=1}^{10000}1(W_{itp}^{(k)}={\displaystyle \max_{p^{*}}W_{itp^{*}}^{(k)})}},\, p=1,\ldots,P
\]
where $1(\cdot)$ is the indicator function that evaluates to 1 if
the expression is true and 0 if false. In other words, we calculate
the proportion of times that the maximum of $W_{itp},\, p=1,\ldots,P$
corresponds to taxon \emph{p}. Considering $\theta_{p}^{(k)}(s_{i}),\, k=1,\ldots,K$,
we have a sample from the posterior of $\theta_{p}(s_{i})$.

@@

\bibitem{pattison1957beginnings}
Pattison WD.
\newblock Beginnings of the American rectangular land survey system, 1784-1800.
\newblock Chicago: University of Chicago; 1957.

@@

\bibitem{gray2012forest}
Gray AN, Brandeis TJ, Shaw JD, McWilliams WH, Miles PD.
\newblock Forest Inventory and Analysis Database of the {United States} of
  {America} ({FIA}).
\newblock Vegetation databases for the 21st century--Biodiversity \& Ecology.
  2012;4:255--264.

@@

\bibitem{Gori:etal:data:2016}
Goring SJ, {University of Wisconsin}.
\newblock Settlement-era gridded tree composition, midwestern {US}: Level 1.
\newblock Long Term Ecological Research Network Data Portal; 2016. http://dx.doi.org/10.6073/pasta/aa0ef9828d41569a96651b056ad89fb3.

\bibitem{Cogb:dataNE:2016}
Cogbill CV.
\newblock Settlement-era tree composition, eastern {US}: level 1.
\newblock Long Term Ecological Research Network; 2016. http://dx.doi.org/10.6073/pasta/e40c1ad172882d5113844296611451f6.

\bibitem{Cogb:dataOH:2016}
Cogbill CV.
\newblock Settlement-era tree composition, {O}hio: level 1.
\newblock Long Term Ecological Research Network; 2016. http://dx.doi.org/10.6073/pasta/d09bb56c6af8ef0783cd7e76f8113b3.

@@

\bibitem{paci:etal:data:2016}
Paciorek CJ, Goring SJ, Thurman AL, Cogbill CV, Williams JW, Mladenoff DJ,
  et~al.
\newblock Settlement-era gridded tree composition, northeastern {US}: level 2.
\newblock Long Term Ecological Research Network; 2016. http://dx.doi.org/10.6073/pasta/8544e091b64db26fdbbbafd0699fa4f9.
